### 2023-02-20 paper/content.tex
Add a caption for figure 1

\begin{equation}
\|\vec{\mathbf{\nabla}}f(x, y, z)\|  = \sqrt{(\partial_x f)^2 + (\partial_y f)^2 + (\partial_z f)^2}\ ,
\end{equation}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{figures/coordinate-system-sketch.png}
\caption{Caption needed.}
\label{fig_coordinate_systems}
\end{figure}

>>>>

\begin{equation}
\|\vec{\mathbf{\nabla}}f(x, y, z)\|  = 
\sqrt{(\partial_x f)^2 + (\partial_y f)^2 + (\partial_z f)^2}
\ ,
\end{equation}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{figures/coordinate-system-sketch.png}
\caption{
Schematic representation of the coordinates systems and modelling elements.
The left panel shows the $x, y, z$ right-handed coordinate system with $z$ 
pointing upward and away from the sample. A dipole with dipole moment vector 
$\mathbf{\vec{m}}$ is also shown at coordinates $(x_c, y_c, z_c)$. The 
observation points are located at regular intervals on an $x-y$ plane. 
The right panel zooms in on the dipole and shows the dipole moment vector
expressed in terms of inclination ($I$, positive downwards), declination
($D$, angle with the $\hat{y}$ direction), and moment magnitude
$m = \|\mathbf{m}\|$.
}
\label{fig_coordinate_systems}
\end{figure}
